Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-08-28 body.tex
Small fix
Tweaks to caption of vary height/order fig

The accuracy of the integration
depends on the number of nodes, or GLQ order,
used in the discretization.
However, \citet{Ku1977} showed
that it also depends on the ratio between
the distance to the computation point
and the distance between adjacent nodes.
Fig.~\ref{fig:sample}
illustrates this effect.
To increase the accuracy of the integration,
one could increase the number of nodes,
as in Fig.~\ref{fig:sample}c.
Likewise,
one could keep the number of nodes fixed
and instead divide the tesseroid into smaller ones.
This would increase the total number of nodes
and effectively decrease
the distance between adjacent nodes.
The latter is the approach
taken by \citet{Li2011}.
Here, we will follow the same approach
and make some improvements to the algorithm.
We will also attempt to quantify
the error committed in the numerical integration.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height and the Gauss-Legendre Quadrature order
        (number of nodes in each dimension).
        The $g_{xy}$ component caused by a
        $7^\circ \times 7^\circ \times 20\ km$ tesseroid
        with $2.67\ g.cm^{-3}$ density
        and top at $z=0$
        was calculated on a regular grid
        at different heights and using different orders.
        The GLQ order used was the same for all three dimensions.
        a) At $400\ km$ height and order 2, the effect is similar to that
        presented by \citet{Asgharzadeh2007}. b) At $150\ km$ height and order
        2, the effect resembles that of four point sources located at the GLQ
        nodes. c) At $150\ km$ but with a higher order of 30, the effect is
        again similar to the maps in \citet{Asgharzadeh2007}.
    }
    \label{fig:sample}
\end{figure*}

>>>>

The accuracy of the integration
depends on the number of nodes, or GLQ order,
used in the discretization.
However, \citet{Ku1977} showed
that it also depends on the ratio between
the distance to the computation point
and the distance between adjacent nodes.
Fig.~\ref{fig:sample}
illustrates this effect
on the $g_{xy}$ gravity gradient component.
To increase the accuracy of the integration,
one could increase the number of nodes,
as in Fig.~\ref{fig:sample}c.
Likewise,
one could keep the number of nodes fixed
and instead divide the tesseroid into smaller ones.
This would increase the total number of nodes
and effectively decrease
the distance between adjacent nodes.
The latter is the approach
taken by \citet{Li2011}.
Here, we will follow the same approach
and make some improvements to the algorithm.
We will also attempt to quantify
the error committed in the numerical integration.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of nodes in the Gauss-Legendre Quadrature
        (i.e., the GLQ order).
        The $g_{xy}$ component was produced by a
        $7^\circ \times 7^\circ \times 20\ km$ tesseroid
        with $2.67\ g.cm^{-3}$ density
        and top at $z=0\ km$.
        The maps were calculated on a regular grid
        with $100\times100$ points.
        The GLQ order used was the same
        in the radial, longitudinal, and latitudial dimensions.
        a) Field calculated at $400\ km$ height using GLQ order 2.
        The effect is similar to that presented by \citet{Asgharzadeh2007}.
        b) At $150\ km$ height and order 2,
        the field resembles that of
        four point sources located at the GLQ nodes.
        This effect was shown by \citet{Ku1977}
        for the case of the $g_z$ component of a right rectangular prism.
        c) At $150\ km$ but with a higher GLQ order of 30,
        the field is similiar to that expected for a single mass source.
    }
    \label{fig:sample}
\end{figure*}
